\section{Motivation and Challenges}
\label{sec:Motivation}

A major issue for \IOT is the rapid growth of the offer, spanning from very simple devices (e.g., temperature, light or sound sensors) to more elaborate objects that interact with their environment (e.g. building security or multimedia solutions). For domestic usage however, it is likely the case that devices would have simpler capabilities, while responding to various scenarios specific to the inhabitants. Therefore, taming the complexity of smart homes requires handling the \emph{interactions} between devices, rather than their own, specific capabilities. 

Even in this context, simple devices could be manipulated in a plethora of scenarios: for example, a simple sensor that simply reports a temperature value could be paired with a heating system to regulate rooms temperature to keep them in comfortable ranges, or detect possible fire situations in the kitchen. 

At a technical level, driving such devices for realising end-users scenarios is hampered by the complexity of vendors and their proprietary data formats, the plethora of \textsc{Api}s that are quickly evolving, and the large variety of communication protocols, among others. This overburden the work of \IOT technicians when dealing with end user requirements. Besides the need for more standardization in \IOT specifications, there is also a crucial need for abstract definition of the semantics of \IOT configurations~\cite{park-16}.

Our proposal consists of two facets. First, we clearly separate the responsibilities of the \emph{technicians}, who deal with the technical details relative to a specific solution deployed in a smart home \cite{park-16}; and \emph{end users}, who control the devices according to their changing, evolving needs. Second, we offer end users a way to interact with their home at an abstract level: far from knowing how each and every device works, users manipulate them only as an abstract level where interactions are carried through events. To this end, we propose that these manipulations occur through a Domain-Specific Language (\DSL).

In this section, we show a typical smart home instalment with affordable, simple devices, then outline the main components of a \DSL that captures \IOT systems. We then list the main challenges such an \IOT \DSL should address to effectively provide a viable solution.

%In domestic configurations, \IOT devices may be used in many different ways for many purposes. These devices are usually used in combination with each other in order to fulfil larger goals required by end users. Furthermore, for the same set of devices, say a temperature sensor and a connected heating system, the way they communicate (or not) can be very dissimilar. For example, in some situations the temperature sensor will regulate the heating system, where in other circumstances, it will be used to prevent fire situations. 

%Considering the wide range of possible use cases for nowadays devices must be coupled to the profusion of vendors, hardware,\textsc{Api}s and so forth, which overburden the work of \IOT technicians when dealing with end user requirements. Besides the need for more standardization in \IOT specifications, there is also a crucial need for abstract definition of the semantics of \IOT configurations~\cite{park-16}. 


\input{Scenarios}
\input{Challenges}
\input{Components}
